\begin{biblio}

\bibitem{Angeli}
Angeli, D. On average performance and stability of economic model predictive control / D. Angeli, R. Amrit, J.B. Rawlings // IEEE transactions on automatic control. -- 2011. -- Vol. 57, № 7. -- P. 1615-1626.

\bibitem{Boyd}
Boyd, S.  Convex optimization / S.P. Boyd, L. Vandenberghe  -- Cambridge university press, 2004.

\bibitem{Diehl}
Diehl M. Lecture Note on Optimal control and Estmation / M. Diehl -- Springer, 2014.

\bibitem{Ellis}
Ellis, M. A tutorial review of economic model predictive control methods / M.~Ellis, H.~Durand, P.D.~Christofides // Journal of Process Control. -- 2014. -- Vol. 24, № 8. -- P. 1156-1178.

\bibitem{Fontes}
Fontes, F.A.C.C. A general framework to design stabilizing nonlinear model predictive controllers / F.A.C.C. Fontes // Systems \& Control Letters. -- 2001. -- Vol. 42, № 2. -- P. 127–143.

\bibitem{Grune}
Grune, L. Nonlinear model predictive control. / L. Grune, J. Pannek -- Springer, 2011.

\bibitem{Mayne}
Rawlings, J.B. Model predictive control: Theory and design / J.B. Rawlings, D.Q. Mayne --  Nob Hill Pub., 2009.


\bibitem{GabasovOLS}
Методы оптимизации: учеб. пособие / В. Альсевич [и др].  -- Минск: <<Четыре четверти>>, 2011.

\bibitem{Kryazhimski}
Асеев, С.М. Принцип максимума Понтрягина и задачи оптимального экономического роста / С.М. Асеев, А.В. Кряжимский // Труды Математического института имени В.А. Стеклова. -- 2007. -- Т. 257. -- 271 с.

\bibitem{Bellman}	
Беллман, Р. Динамическое программирование / Р. Беллман. -- М.:~Иностранная литература, 1960. -- 400 с.

\bibitem{Pontryagin}
Математическая теория оптимальных процессов / Л.С. Понтрягин, В.Г.~Болтянский, Р.В.~Гамкрелидзе, Е.Ф.~Мищенко  -- М.: Физматгиз, 1961. 392~с.






\end{biblio} 